### 2018-01-22 includes/prior.tex
Addressing Federico's feedback. Adding Makefile target to re-gather data.

\section{Prior Work}

    There are several fuzzers and problem generators currently available, but none of them support string or regex generation or transformation. For example the FuzzSMT\cite{fuzzsmt} tool generates \smt{} problems with bit vectors and arrays, but does not support strings or regexes. The SMTpp\cite{smtpp} tool preprocesses and simplifies problems, but does not generate new ones or fuzz existing ones.

>>>>

\section{Related Work}

    Naturally, many solver developers author their own test suites to validate their solvers \cite{cvc4-tests} \cite{z3str3-tests} \cite{z3str2-tests}. In addition, several popular problem suites are publicly available for solver validation, such as the Kaluza \cite{kaluza} and Kausler \cite{kausler} suites.

    There are likewise several fuzzers and problem generators currently available, but none of them can generate or transform string and regex problems. For example the FuzzSMT\cite{fuzzsmt} tool generates \smt{} problems with bit vectors and arrays, but does not support strings or regexes. The SMTpp\cite{smtpp} tool preprocesses and simplifies problems, but does not generate new ones or fuzz existing ones.

### 2018-01-22 includes/problems.tex
Addressing Federico's feedback. Adding Makefile target to re-gather data.

    We generated several suites of string and regex problems using \fuzzer{}, and they are available at \problemRepo{}. The \texttt{generated} suite contains problems that were generated using \generator{}, described below:

@@

        This section describes the bugs in \us{} that were discovered (and subsequently fixed) by testing it with the \fuzzer{} problem suites.

@@

        While the aforementioned suites are useful in analysing a solver, we also found that randomisation was helpful in exploratory debugging, and we encourage this pattern as well. For example the following usage can feed random problems to \cvc{} until it returns an error:

        {\scriptsize\begin{verbatim}
while stringfuzzg random | cvc4 --lang smt2.5 --tlimit=5000; do sleep 0; done\end{verbatim}}

>>>>

    We generated several suites of string and regex problems using \fuzzer{}. These problems are available at \problemRepo{}. Below, we describe the \texttt{generated} suite that we generated using \generator{}:

@@

        This section describes the bugs we discovered in \us{} (that were subsequently fixed) by testing it with the \fuzzer{} problem suites.

@@

        While the aforementioned suites are useful in analysing a solver, we also used randomised \fuzzer{} runs for exploratory debugging. For example the following usage can feed random problems to \cvc{} until it returns an error:

        {\scriptsize\begin{verbatim}
while stringfuzzg -r random | tee problem.smt25 | cvc4 --lang smt2.5 --tlimit=5000; do
    sleep 0
done\end{verbatim}}
